Meta-analysis

### 2019-11-20 05_MetaAnalysis.Rmd
Added the imputation of MSE

```{r LME_slimmer_cluster_disease_mod}
library(lme4)
slimmer_PM_dat <- read.csv("data/slimmer_PM_clusterdat.csv")

@@

@@

slimmer_PM_dat$yi <- slimmer_PM_dat$grain_yield.t.ha
slimmer_PM_dat$vi <- slimmer_PM_dat$yield_error

@@

PM_mv_AI <- rma.mv(yi,vi,
                   mods = ~ spray_management,
#                   method = "ML",
                   random = list(~ spray_management | trial),
                   struct = "UN",
                   data = slimmer_PM_dat)

>>>>

```{r LME_slimmer_cluster_disease_mod}
library(lme4)
slimmer_PM_dat <- read.csv("data/slimmer_PM_clusterdat.csv")
unique(slimmer_PM_dat$trial_ref, slimmer_PM_dat$location, slimmer_PM_dat$year)

@@

```{r imputing_MSE}
hist(unique(slimmer_PM_dat$Y_Msquare))
hist(log(unique(slimmer_PM_dat$Y_Msquare))) # log mean square has a more normal distribution

TrialMSQ <- slimmer_PM_dat %>%
   group_by(trial_ref)%>%
   summarise(unique(Y_Msquare))

TrialMSQ[is.na(TrialMSQ$`unique(Y_Msquare)`), "trial_ref"]

for(i in TrialMSQ[is.na(TrialMSQ$`unique(Y_Msquare)`),]$trial_ref){
   slimmer_PM_dat[slimmer_PM_dat$trial_ref == i,"Y_Msquare"] <- 
      exp(
         rnorm(n = 1,
               mean = mean(TrialMSQ$`unique(Y_Msquare)`, na.rm = TRUE),
               sd(TrialMSQ$`unique(Y_Msquare)`, na.rm = TRUE)
         )
      )
   }

@@

slimmer_PM_dat$yi <- slimmer_PM_dat$grain_yield.t.ha
slimmer_PM_dat$vi <- slimmer_PM_dat$Y_Msquare/(slimmer_PM_dat$n * slimmer_PM_dat$grain_yield.t.ha^2)

@@

PM_mv_AI <- rma.mv(yi,vi,
                   mods = ~ spray_management,
                   method = "ML",
                   random = list(~ spray_management | trial),
                   struct = "UN",
                   data = slimmer_PM_dat)
